The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2025-04-25 donde.tex
revisions for r3
First set of edits after R&R

\begin{figure}[htbp]    
\begin{center}
\includegraphics[width=0.9\textwidth]{Figuras/consort.pdf}
  \end{center}
 \caption{Experiment description}
     \label{exp_description}
%\textit{Do file: }  \texttt{ss\_att.do}
\end{figure}

@@

\begin{table}[!h]
\caption{Summary statistics and Balance}
\label{SS}
\begin{center}
\resizebox{0.65\textwidth}{!}{
\scriptsize{\input{./Tables/SS.tex}}
}
\end{center}
\scriptsize {This table has two panels. Panel A uses administrative data at the loan level, while Panel B uses survey data. Each row in this table corresponds to a regression, where the level of observation is the individual loan originated. The dependent variables of these regressions are displayed in the first column. Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice). The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients. The admin data was a very limited set of pre-determined variables. The dependent variables in Panel A are the loan amount in pesos, and an indicator for whether the day of the loan origination was a weekday (as opposed to weekend). The dependent variables in Panel B from the survey (see the questions in Table \ref{baseline_survey}. Subjective value of the pawn (how much would the client be willing to sell it for (Q3), an indicator for having trouble paying bills in the last 6-months (Q28), present bias (constructed from questions Q10 and Q29 in the standard way as in \cite{Ashraf}), an indicator for whether they make expenses budget for the month ahead of time. The subjective probability of recovery was elicited a la Manski (from 0 to 100 what is the probability that you will recoup your pawn), pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$) age is in year, +High-school is a dummy that indicates if the client has completed high school. 
}
%\textit{Do file: } \texttt{ss\_att.do}
\end{table}

@@

\begin{figure}
    \begin{center}
        \centering
        \includegraphics[width=1.0\textwidth]{Figuras/tot_tut_intuition.png}
    \end{center}
 \caption{The Controlled Choice Design.}
 \scriptsize{This figure provides graphical intuition for the way in which the controlled choice design from Section point identifies both the treatment on the treated (TOT) and treatment on the untreated (TUT) effects, as discussed in Section \ref{sec:randchoice} and \ref{append:randchoice}. 
    The gray shaded regions denote borrowers with a commitment contract; the white shaded regions denote borrowers with a status quo contract.
    A comparison of means across control and forcing arms identifies the ATE of forcing  commitment.
    The TOT and TUT effects of commitment are identified as follows.
    In the choice arm, anyone with a commitment contract is a chooser; in the control and forcing arms, we do not know who is a chooser and who is not.
    Because borrowers are randomly assigned to experimental treatment arms, however, the share of choosers will be the same, on average, across experimental arms.
    This is depicted using dashed vertical lines in the control and forcing arms.
    This overall share of choosers and non-choosers is point identified from the choice arm.
    Now, the difference of mean outcomes across the choice and control arms gives the intent-to-treat effect of offering choice.
    Under the exclusion restriction that moving non-choosers between the choice and forcing arms does not change their outcomes, this comparison ``nets out'' the non-choosers.
    Hence, the ITT of offering choice equals the TOT multiplied by the share of choosers. 
    Similarly, under the exclusion restriction that moving choosers between the choice and forcing arm does not affect their outcomes, the difference of means across the forcing and choice arms ``nets out'' the choosers and hence equals the TUT multiplied by the share of non-choosers.}
    \label{tot_tut_graph}
     %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
\end{figure}

@@

A behavioral literature has highlighted voluntary commitment as an attractive way of allowing the ``right'' people to self-select. % A discussion of compulsory commitment is necessarily paternalistic, and by its nature focuses on impacts among those who would not have selected commitment voluntarily. 
%Viewed through the lens of rational choice theory, it is unsurprising that we estimate $\text{TOT}>\text{TUT}$. 
The argument for compulsory treatment, centers on the surprising result that $\text{TUT}>0$. We now investigate several potential explanations for this result.
For simplicity, we focus on causal effects for the APR outcome throughout this section. We view this section as an exploratory analysis to stimulate ideas for future research. We examine four potential explanations for the positive $\text{TUT}$: the need to learn, time discounting, present bias, and overconfidence.  To explore the last two dimensions we will use survey data.\footnote{Since merging with survey data reduces our sample, Table \ref{TUT_cond_survet} demonstrates that the subsample on whom we have survey data appears to be representative in terms of treatment effects.}

>>>>

\begin{figure}[htbp]    
\begin{center}
\includegraphics[width=0.9\textwidth]{Figuras/consort.pdf}
  \end{center}
 \caption{Experiment description}
     \label{exp_description}
%\textit{Do file: }  \texttt{consort.do}
\end{figure}

@@

\begin{table}[!h]
\caption{Summary statistics and Balance}
\label{SS}
\begin{center}
\resizebox{0.65\textwidth}{!}{
\scriptsize{\input{./Tables/SS.tex}}
}
\end{center}
\scriptsize {This table has two panels. Panel A uses administrative data at the loan level, while Panel B uses survey data. Each row in this table corresponds to a regression, where the level of observation is the individual loan originated. The dependent variables of these regressions are displayed in the first column. Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice). The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients. The admin data was a very limited set of pre-determined variables. The dependent variables in Panel A are the loan amount in pesos, and an indicator for whether the day of the loan origination was a weekday (as opposed to weekend). The dependent variables in Panel B from the survey (see the questions in Table \ref{baseline_survey}. Subjective value of the pawn (how much would the client be willing to sell it for (Q3), an indicator for having trouble paying bills in the last 6-months (Q28), present bias (constructed from questions Q10 and Q29 in the standard way as in \cite{Ashraf}), an indicator for whether they make expenses budget for the month ahead of time. The subjective probability of recovery was elicited a la Manski (from 0 to 100 what is the probability that you will recoup your pawn), pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$) age is in year, +High-school is a dummy that indicates if the client has completed high school. 
}
%\textit{Do file: } \texttt{ss\_balance.do}
\end{table}

@@

\begin{figure}
    \begin{center}
        \centering
        \includegraphics[width=1.0\textwidth]{Figuras/tot_tut_graph.png}
    \end{center}
 \caption{The Controlled Choice Design.}
 \scriptsize{This figure provides graphical intuition for the way in which the controlled choice design from Section point identifies both the treatment on the treated (TOT) and treatment on the untreated (TUT) effects, as discussed in Section \ref{sec:randchoice} and \ref{append:randchoice}. 
    The gray shaded regions denote borrowers with a commitment contract; the white shaded regions denote borrowers with a status quo contract.
    A comparison of means across control and forcing arms identifies the ATE of forcing  commitment.
    The TOT and TUT effects of commitment are identified as follows.
    In the choice arm, anyone with a commitment contract is a chooser; in the control and forcing arms, we do not know who is a chooser and who is not.
    Because borrowers are randomly assigned to experimental treatment arms, however, the share of choosers will be the same, on average, across experimental arms.
    This is depicted using dashed vertical lines in the control and forcing arms.
    This overall share of choosers and non-choosers is point identified from the choice arm.
    Now, the difference of mean outcomes across the choice and control arms gives the intent-to-treat effect of offering choice.
    Under the exclusion restriction that moving non-choosers between the choice and forcing arms does not change their outcomes, this comparison ``nets out'' the non-choosers.
    Hence, the ITT of offering choice equals the TOT multiplied by the share of choosers. 
    Similarly, under the exclusion restriction that moving choosers between the choice and forcing arm does not affect their outcomes, the difference of means across the forcing and choice arms ``nets out'' the choosers and hence equals the TUT multiplied by the share of non-choosers.}
    \label{tot_tut_graph}
     %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
\end{figure}

@@

A behavioral literature has highlighted voluntary commitment as an attractive way of allowing the ``right'' people to self-select. % A discussion of compulsory commitment is necessarily paternalistic, and by its nature focuses on impacts among those who would not have selected commitment voluntarily. 
%Viewed through the lens of rational choice theory, it is unsurprising that we estimate $\text{TOT}>\text{TUT}$. 
The argument for compulsory treatment, centers on the surprising result that $\text{TUT}>0$. We now investigate several potential explanations for this result.
For simplicity, we focus on causal effects for the APR outcome throughout this section. We view this section as an exploratory analysis to stimulate ideas for future research. We examine four potential explanations for the positive $\text{TUT}$: the need to learn, time discounting, present bias, and overconfidence.  To explore the last two dimensions we will use survey data.\footnote{Since merging with survey data reduces our sample, Table \ref{TUT_cond_survey} demonstrates that the subsample on whom we have survey data appears to be representative in terms of treatment effects.}
